TCGA

### 2017-11-20 inst/SurvivalTCGA/processTCGA.Rmd
adding processTCGA script

#subset expression list to only include in common genes
cpmFiltered <- lapply(cpm, function(x) as.data.frame(x[rownames(x) %in% inCommon, ]))

#bind list
cpmMat <- as.matrix(bind_cols(cpmFiltered))

>>>>

#subset expression list to only include in common genes
cpmFiltered <- lapply(cpm, function(x) as.data.frame(x[rownames(x) %in% inCommon, ]))
rm(cpm)

#bind list
cpmMat <- as.matrix(dplyr::bind_cols(cpmFiltered))
rm(cpmFiltered)
